---
title: "Test"
author: "Daniel Pinckney"
date: '2025-04-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(countrycode)
library(CoordinateCleaner)
library(dplyr)
library(ggplot2)
library(rgbif)
library(sf)
library(rnaturalearth)
```

## R Markdown

This is a Test R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. I am embedding R code chunks like this:

```{r load data}
dat <- occ_search(scientificName = "Paranuncia gigantea", 
                  limit = 5000, 
                  hasCoordinate = TRUE)

dat <- dat$data
```

## Including Plots

You can also embed plots, for example:

```{r filter columns}
dat <- dat %>%
  dplyr::select(species, decimalLongitude, 
                decimalLatitude, countryCode, individualCount,
                gbifID, family, taxonRank, coordinateUncertaintyInMeters,
                year, basisOfRecord, institutionCode, datasetName)
```

```{r clean step one}
dat <- dat %>%
  filter(!is.na(decimalLongitude)) %>%
  filter(!is.na(decimalLatitude))
```

```{r clean step two}
dat <- dat %>%
  filter(decimalLongitude != 0) %>%
  filter(decimalLatitude != 0)
```

```{r convert country codes}
dat$countryCode <-  countrycode(dat$countryCode, 
                                origin =  'iso2c',
                                destination = 'iso3c')
```

```{r world map}
wm <- borders("world", colour = "gray50", fill = "gray50")
ggplot() +
  coord_fixed() +
  wm +
  geom_point(data = dat,
             aes(x = decimalLongitude, y = decimalLatitude),
             colour = "darkred",
             size = 0.5) +
  theme_bw()
```
```{r Tasmania map}
Tasm <- borders("world", regions = "Australia:tasmania", colour = "gray50", fill = "gray50")
ggplot() +
  coord_fixed() +
  Tasm +
  geom_point(data = dat,
             aes(x = decimalLongitude, y = decimalLatitude),
             colour = "darkred",
             size = 0.5) +
  theme_bw()
```
```{r Aus map}
Ausm <- borders("world", regions = "Australia", colour = "gray50", fill = "gray50")
ggplot() +
  coord_fixed() +
  Ausm +
  geom_point(data = dat,
             aes(x = decimalLongitude, y = decimalLatitude),
             colour = "darkred",
             size = 0.5) +
  theme_bw()
```

```{r full package clean}
dat <- data.frame(dat)
flags <- clean_coordinates(x = dat, 
                           lon = "decimalLongitude", 
                           lat = "decimalLatitude",
                           countries = "countryCode",
                           species = "species",
                           tests = c("capitals", "centroids",
                                    "equal", "zeros", "countries"))
```
```{r}
summary(flags)
plot(flags, lon = "decimalLongitude", lat = "decimalLatitude")
```


```{r}
names(dat)[2:3] <- c("decimalLongitude", "decimalLatitude")

clean <- dat %>%
  cc_zero()
```

